% !TeX root=../main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\latinuniversity{University of Tehran}
\latincollege{College of Engineering}
\latinfaculty{Faculty of Electrical and Computer Engineering}
\latindepartment{Software Department}
\latinsubject{Computer Engineering}
\latinfield{Software Engineering}
\latintitle{Cappu, a platform to mint and transfer data NFTs}
\firstlatinsupervisor{Dr. Ehsan Khamespanah}
% \secondlatinsupervisor{Second Supervisor}
% \firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Amin}
\latinsurname{Bashiri}
\latinthesisdate{June 2022}
\latinkeywords{Cappu, NFT, Smart-Contract, Solidity, ERC721}
\en-abstract{
  The objective of this project is to develop Cappu, an easy-to-use open-source\LTRfootnote{https://github.com/bshramin/cappu} platform that enables individuals and organizations to mint and transfer NFTs.
  Assets such as cars, houses, movie tickets, and doctor appointments can be minted, sold, and transferred to others as NFTs.\newline \indent
  Despite the fact that Cappu has a variety of uses, the primary objective of this project is to familiarize ourselves with the process and tools involved in developing and deploying smart contracts, to develop and connect the front end of the smart contract, and to become familiar with the standards of building smart contracts, such as ERC721 and ERC1155.\newline \indent
  Web3 is the next step in the evolution of the Internet, the most important technological advancement after the World Wide Web.
  Cryptocurrencies, consensus algorithms, and smart contracts will allow for a greater degree of decentralization in applications and financial transactions.\newline \indent
  One of the major advantages of a decentralized Internet is the absolute ownership of assets.
  It is designed to ensure that no one individual or organization can interfere with another's assets or prevent them from being transferred.
  Digital assets will also be protected by the blockchain.
  Even if a person copies an artist's digital artwork, it is still evident to everyone that the artist owns the image.\newline \indent
  Non-fungible tokens became very popular due to the advantages of ownership they provide.
  Moreover, the ease and convenience of minting, keeping, selling, and transferring NFTs has contributed to the wide adoption of these tokens.
  There have been many technologies and platforms introduced and are still being developed for this new ecosystem.\newline \indent
}
